Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-02 paper/disc20clustering.tex
Lower bound & table asymptotic

\begin{table*}
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\ell - 3/2$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $54\cdot \ell $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $(k\cdot \ell - k - \ell) / 2$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell \cdot \min \{ k \cdot \ell, \Rep(k, \ell) \})$\hspace{0.3cm} (\S \ref{sec:k3}) \\
		\rowcolor{gray!25}
		Perfect partition & $(k\cdot \ell - k - \ell) / 2$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$2(k -1 )\cdot \ell$\hspace{0.3cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and the results provided in this paper. By $\Rep$ we denote the cost of a single component repartition, and we elaborate on this in Section~\ref{sec:k3}
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}

@@

\maciek{Eviction - introduce.}

@@

\maciek{TODO: Intro to the learning problem is missing. What is the problem definition. How is it different from the general problem. Emphasize the fact that OPT is constrained not to migrate.}

At the end of this section, we discuss an asymptotically optimal upper bound.

@@

\noindent
\textbf{Remark on resource augmentation.}
The majority of work on Online Balanced Partitioning so far (todo: cite) focuses on the scenario with resource augmentation.
We note that this lower bound provides insights into this scenario as well.
Consider an instance with $k$ divisible by $3$, and construct $3$ ground sets of size $k/3$ in each cluster.
Then, apply the construction from the lower bound for $k=3$, now treating these ground sets in the way we used individual nodes.
For the resource augmentation as large as $1+1/3-\epsilon$, no more than $3$ such ground sets fit in one cluster.
The cost of any algorithm (including \OPT) scales up by $k/3$, and the lower bound $\Omega(\ell)$ holds.

@@

\section{The Online Problem}
\label{sec:k3}

\maciek{Not precise name? Both the learning problem and the general one is online.}

@@

\subsection{Improved analysis of the component-based algorithm}

>>>>

\begin{table*}
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\Omega(\ell)$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $O(\ell) $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell \cdot \min \{ k \cdot \ell, \Rep(k, \ell) \})$\hspace{0.1cm} (\S \ref{sec:k3}) \\
		\rowcolor{gray!25}
		Learning model & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell)$\hspace{0.3cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and the results provided in this paper. By $\Rep$ we denote the cost of a single component repartition, and we elaborate on this in Section~\ref{sec:k3}. The results pertain to the general partitioning model, but the last row, that pertains to the learning model for arbitrary $k$ and $\ell$.
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}

@@

\maciek{Eviction - introduce the concept.}

@@

In this section we consider a variant of Online Balanced Partitioning, where requests are permanent: once a pair of nodes start communicating, they continue forever.
Each communicating pair must be collocated, as otherwise the cost would be infinite.
We study the instances with finite cost: where the communication graph can be perfectly partitioned in the clusters.

For this setting, we show a surprisingly high lower bound of $\Omega(k \cdot \ell)$.
The lower bound can be easily translated to the partitioning model (Section~\ref{sec:part}) with finite request sequence.
At the end of this section, we discuss an asymptotically optimal upper bound.

@@

We conclude by emphasizing the generality of the lower bound.

\noindent
\textbf{General partitioning problem.}
Every lower bound for the learning problem constitutes a valid lower bound for the partitioning problem.
The bound for partitioning converges to the bound for learning as the input sequence grows.

Our construction allows for an exact lower bound for partitioning with finite input sequence.
To this end, we issue only enough requests until the algorithm collocates the nodes of each ground set.
If it never does, we repeat until it pays $k\cdot \ell$.

\noindent
\textbf{Resource augmentation.}
The majority of work on Online Balanced Partitioning so far (todo: cite) focuses on the scenario with resource augmentation.
We note that this lower bound provides insights into this scenario as well.

Consider an instance with $k$ divisible by $3$, and construct $3$ ground sets of size $k/3$ in each cluster.
Then, apply the construction from the lower bound for $k=3$, now treating these ground sets in the way we used individual nodes.
For the resource augmentation as large as $1+1/3-\epsilon$, no more than $3$ such ground sets fit in one cluster.
The cost of any algorithm (including \OPT) scales up by $k/3$, and the lower bound $\Omega(\ell)$ holds.

@@

\section{The Partitioning Problem}
\label{sec:part}

@@

\subsection{Improved analysis of the component-based algorithm}
\label{sec:k3}
